Open-Set Domain Adaptation through Self-Supervision

### 2022-02-13 paper/main.tex
add image step 1
Updated results table

@@

The results show that self-supervision technique can help in domain adaptation task and open-set classification tasks.
A few critical points still remain on our method of study and proposed solution.
The most important one is probably parameter choosing for different models, as we have seen that variations cause huge differences in results and sequential optimization of parameter is a sub-optimal heuristic.
Furthermore, having the model to learn two different tasks at once, it could be useful to use a slower learning model at the expense of longer training times.

@@

\begin{table}
  \centering
  \begin{tabular}[h]{||c|c|c||c||}
    \hline
    \multicolumn{4}{||c||}{OFF-OFF} \\
    \hline
    $\alpha_1$ & $\mathcal{\tilde N}$ & $\alpha_2$ & HOS$_{mean}$\\    
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\alpha_1$} \\
    \hline
    {\bf 1.0}  & \multirow{4}{*}{0.6} & \multirow{4}{*}{3.0} & {\bf 40.27\%} \\
    3.0  & & & 22.69\% \\
    5.0  & & & 18.78\% \\
    10.0 & & & 9.99\% \\
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\mathcal{\tilde N}$} \\
    \hline
    \multirow{4}{*}{1.0} & 0.50 & \multirow{4}{*}{3.0}  & 28.05\%\\
    & 0.55 & & 34.73\% \\
    & 0.60 & & 40.27\% \\
    & 0.65 & & 43.16\% \\
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\alpha_2$} \\
    \hline
    \multirow{7}{*}{1.0} & \multirow{7}{*}{0.7} & 0.1 & 42.79\%\\
    && 1.0 & 44.35\% \\
    && 2.0 & 43.53\% \\
    && {\bf 3.0} & {\bf 44.38}\% \\
    && 4.0 & 43.12\% \\
    && 5.0 & 41.97\% \\
    && 10.0 & 42.01\% \\
    \hline
  \end{tabular}
  \caption{\centering\label{tab:ablationoffoff} Hyperparameters picking process for configuration Multi-Head Off and Center-Loss Off}
\end{table}

@@

\begin{table*}
  \centering
  \begin{tabular}[t]{||c||c|c|c|c||c|c|c|c||c|c|c|c||}
    \hline
    \multicolumn{13}{||c||}{Results} \\
    \hline
    \multirow{2}{*}{Shift}   & \multicolumn{4}{|c||}{Single-Head, No Center Loss} & \multicolumn{4}{|c||}{Multi-Head, No Center Loss} & \multicolumn{4}{|c||}{Multi-Head, Center Loss} \\
            & AUROC & HOS   & UNK   & OS*   & AUROC & HOS   & UNK   & OS*   & AUROC & HOS   & UNK   & OS*   \\
    \hline
    A$\to$C & 52.07 & 44.76 & 58.65 & 36.19 & 57.46 & 46.64 & 62.95 & 37.04 & 59.77 & 52.68 & 62.73 & 45.40 \\
    A$\to$P & 50.84 & 51.27 & 57.56 & 46.23 & 56.31 & 54.13 & 60.42 & 49.03 & 56.86 & 52.46 & 63.35 & 44.77 \\
    A$\to$R & ??.?? & ??.?? & ??.?? & ??.?? & 59.88 & 56.60 & 53.18 & 60.65 & 58.86 & 61.67 & 66.82 & 57.26 \\
    C$\to$A & 49.52 & 41.74 & 43.10 & 40.47 & 55.28 & 42.63 & 51.57 & 36.33 & 55.76 & 46.84 & 60.19 & 38.35 \\
    C$\to$P & 54.42 & 46.99 & 41.51 & 54.15 & 59.13 & 51.88 & 60.03 & 45.69 & 58.35 & 52.69 & 62.19 & 45.72 \\
    C$\to$R & 53.43 & 46.18 & 38.64 & 57.39 & 60.75 & 56.00 & 61.29 & 51.63 & 59.15 & 55.97 & 63.18 & 50.25 \\
    P$\to$A & 48.32 & 37.07 & 33.70 & 41.20 & 55.62 & 41.72 & 48.90 & 36.39 & 53.50 & 40.97 & 49.53 & 34.94 \\
    P$\to$C & 47.76 & 43.99 & 48.42 & 40.31 & 56.77 & 46.10 & 55.11 & 39.65 & ??.?? & ??.?? & ??.?? & ??.?? \\
    P$\to$R & 50.37 & 34.14 & 22.88 & 67.27 & 59.68 & 48.41 & 40.91 & 59.30 & 61.10 & 56.22 & 56.89 & 55.58 \\
    R$\to$A & 49.39 & 25.08 & 15.99 & 58.19 & 58.47 & 45.00 & 39.50 & 52.43 & 57.98 & 48.92 & 45.61 & 52.77 \\
    R$\to$C & 49.80 & 46.70 & 48.27 & 45.23 & 57.02 & 49.00 & 42.82 & 57.34 & 57.09 & 48.69 & 61.11 & 40.47 \\
    R$\to$P & 54.10 & 23.37 & 13.89 & 73.69 & 62.33 & 50.31 & 39.51 & 69.27 & 63.96 & 59.64 & 54.40 & 66.02 \\
    \hline
    AVG     & ??.?? & ??.?? & ??.?? & ??.?? & 52.23 & 49.03 & 51.35 & 49.56 & ??.?? & ??.?? & ??.?? & ??.?? \\ 
    \hline
  \end{tabular}
  \caption{\centering\label{tab:results}Results for each configuration and each domain shift. All values are percentages.}
\end{table*}

>>>>

\begin{figure*}
  \includegraphics[width=\textwidth ]{scheme_step1.png}
  \caption{\label{fig:separation} Schema representing the step 1 training}
\end{figure*}

@@

The results show that self-supervision technique can help in domain adaptation task and open-set classification tasks.
A few critical points still remain on our method of study and proposed solution.
The most important one is probably parameter choosing for different models, as we have seen that variations cause huge differences in results and sequential optimization of parameter is a sub-optimal heuristic.
Furthermore, having the model to learn two different tasks at once, it could be useful to use a slower learning model at the expense of longer training times.
Another observation that we can make based 
on gathered data is the impact that the threshold 
choice have during the target separation step.
This is ascrivable to a weak normality score 
that may need particular attention in order to develop
a model able to reduce negative transfer.

@@

\begin{table}
  \centering
  \begin{tabular}[h]{||c|c|c||c||}
    \hline
    \multicolumn{4}{||c||}{OFF-OFF} \\
    \hline
    $\alpha_1$ & $\mathcal{\tilde N}$ & $\alpha_2$ & HOS$_{mean}$\\    
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\alpha_1$} \\
    \hline
    {\bf 1.0}  & \multirow{4}{*}{0.6} & \multirow{4}{*}{3.0} & {\bf 40.27\%} \\
    3.0  & & & 22.69\% \\
    5.0  & & & 18.78\% \\
    10.0 & & & 9.99\% \\
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\mathcal{\tilde N}$} \\
    \hline
    \multirow{6}{*}{1.0} & 0.50 & \multirow{6}{*}{3.0}  & 28.05\%\\
    & 0.55 & & 34.73\% \\
    & 0.60 & & 40.27\% \\
    & 0.65 & & 43.16\% \\
    & {\bf 0.70} & & {\bf 44.38\%} \\
    & 0.75 & & 43.87\% \\
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\alpha_2$} \\
    \hline
    \multirow{7}{*}{1.0} & \multirow{7}{*}{0.7} & 0.1 & 42.79\%\\
    && 1.0 & 44.35\% \\
    && 2.0 & 43.53\% \\
    && {\bf 3.0} & {\bf 44.38}\% \\
    && 4.0 & 43.12\% \\
    && 5.0 & 41.97\% \\
    && 10.0 & 42.01\% \\
    \hline
  \end{tabular}
  \caption{\centering\label{tab:ablationoffoff} Hyperparameters picking process for configuration Multi-Head Off and Center-Loss Off}
\end{table}

@@

\begin{table*}
  \centering
  \begin{tabular}[t]{||c||c|c|c|c||c|c|c|c||c|c|c|c||}
    \hline
    \multicolumn{13}{||c||}{Results} \\
    \hline
    \multirow{2}{*}{Shift}   & \multicolumn{4}{|c||}{Single-Head, No Center Loss} & \multicolumn{4}{|c||}{Multi-Head, No Center Loss} & \multicolumn{4}{|c||}{Multi-Head, Center Loss} \\
            & AUROC & HOS   & UNK   & OS*   & AUROC & HOS   & UNK   & OS*   & AUROC & HOS   & UNK   & OS*   \\
    \hline
    A$\to$C & 52.07 & 44.76 & 58.65 & 36.19 & 57.46 & 46.64 & 62.95 & 37.04 & 59.77 & 52.68 & 62.73 & 45.40 \\
    A$\to$P & 50.84 & 51.27 & 57.56 & 46.23 & 56.31 & 54.13 & 60.42 & 49.03 & 56.86 & 52.46 & 63.35 & 44.77 \\
    A$\to$R & 27.94 & 68.13 & 17.58 & 52.25 & 59.88 & 56.60 & 53.18 & 60.65 & 58.86 & 61.67 & 66.82 & 57.26 \\
    C$\to$A & 49.52 & 41.74 & 43.10 & 40.47 & 55.28 & 42.63 & 51.57 & 36.33 & 55.76 & 46.84 & 60.19 & 38.35 \\
    C$\to$P & 54.42 & 46.99 & 41.51 & 54.15 & 59.13 & 51.88 & 60.03 & 45.69 & 58.35 & 52.69 & 62.19 & 45.72 \\
    C$\to$R & 53.43 & 46.18 & 38.64 & 57.39 & 60.75 & 56.00 & 61.29 & 51.63 & 59.15 & 55.97 & 63.18 & 50.25 \\
    P$\to$A & 48.32 & 37.07 & 33.70 & 41.20 & 55.62 & 41.72 & 48.90 & 36.39 & 53.50 & 40.97 & 49.53 & 34.94 \\
    P$\to$C & 47.76 & 43.99 & 48.42 & 40.31 & 56.77 & 46.10 & 55.11 & 39.65 & 58.64 & 46.81 & 60.95 & 37.99 \\
    P$\to$R & 50.37 & 34.14 & 22.88 & 67.27 & 59.68 & 48.41 & 40.91 & 59.30 & 61.10 & 56.22 & 56.89 & 55.58 \\
    R$\to$A & 49.39 & 25.08 & 15.99 & 58.19 & 58.47 & 45.00 & 39.50 & 52.43 & 57.98 & 48.92 & 45.61 & 52.77 \\
    R$\to$C & 49.80 & 46.70 & 48.27 & 45.23 & 57.02 & 49.00 & 42.82 & 57.34 & 57.09 & 48.69 & 61.11 & 40.47 \\
    R$\to$P & 54.10 & 23.37 & 13.89 & 73.69 & 62.33 & 50.31 & 39.51 & 69.27 & 63.96 & 59.64 & 54.40 & 66.02 \\
    \hline
    AVG     & 49.00 & 42.45 & 36.68 & 51.05 & 52.23 & 49.03 & 51.35 & 49.56 & 58.42 & 51.96 & 58.91 & 47.46 \\ 
    \hline
  \end{tabular}
  \caption{\centering\label{tab:results}Results for each configuration and each domain shift. All values are percentages.}
\end{table*}
